01-deseq2

### 2019-03-14 scripts/01-DESeq2-all.Rmd
slim to all, rename all

```{r}
colData <- read.csv("../results/00-colData_characterization.csv", header = T, row.names = 1)
countData <- read.csv("../results/00-countData_characterization.csv", header = T, row.names = 1)
```

```{r deseq2}
dds <- DESeqDataSetFromMatrix(countData, colData, ~ sex*treatment)
dds # view the DESeq object - note numnber of genes
dds <- dds[ rowSums(counts(dds)) > 1, ]  # Pre-filtering genes with 0 counts
dds # view number of genes afternormalization and the number of samples
dds <- DESeq(dds) # Differential expression analysis
vsd <- vst(dds, blind=FALSE) ## variance stabilized
#head(assay(vsd),3)
#write.csv(assay(vsd), file = "../results/01-vsd.csv", row.names = T)
```

@@

res_summary(c("sex", "female", "male"))
res_summary(c("treatment", "hatch", "control"))
```

@@

summary(aov(PC1 ~ sex * treatment * tissue, data=pcadata)) 
summary(aov(PC2 ~ sex * treatment * tissue, data=pcadata))

@@

pdf(file="../figures/01-pcaplot12.pdf", width=3.3, height=2.5)
plot(PCA12)
dev.off()

```

Now, I'll do RNAseq on all the data

```{r deseq2}
dds <- DESeqDataSetFromMatrix(countHyp, colHyp, ~ treatment)
dds # view the DESeq object - note numnber of genes
dds <- dds[ rowSums(counts(dds)) > 1, ]  # Pre-filtering genes with 0 counts
dds # view number of genes afternormalization and the number of samples
dds <- DESeq(dds) # Differential expression analysis
vsd <- vst(dds, blind=FALSE) ## variance stabilized
#head(assay(vsd),3)
#write.csv(assay(vsd), file = "../results/01-vsd.csv", row.names = T)
```

res_summary(c("sex", "female", "male"))
res_summary(c("treatment", "hatch", "control"))
```

```{r pca}
# create the dataframe using my function pcadataframe
pcadata <- pcadataframe(vsd, intgroup=c("treatment"), returnData=TRUE)

percentVar <- round(100 * attr(pcadata, "percentVar"))

summary(aov(PC1 ~ treatment, data=pcadata)) 
summary(aov(PC2 ~  treatment , data=pcadata))

PCA12 <- ggplot(pcadata, aes(pcadata$PC1, pcadata$PC2, color=treatment)) +
    geom_point(size=1.5) +
    xlab(paste0("PC1: ", percentVar[1],"%")) +
    ylab(paste0("PC2: ", percentVar[2],"%")) +
    stat_ellipse(level = 0.95) + 
    theme_cowplot(font_size = 7, line_size = 0.25)  +
  labs(title ="Female Hypothalamus")
PCA12

```

>>>>

```{r}
colData <- read.csv("../results/00-colData-characterization.csv", header = T, row.names = 1)
countData <- read.csv("../results/00-countData-characterization.csv", header = T, row.names = 1)
```

```{r deseq2}
dds <- DESeqDataSetFromMatrix(countData, colData, ~ sex*treatment*tissue)
dds # view the DESeq object - note numnber of genes
dds <- dds[ rowSums(counts(dds)) > 1, ]  # Pre-filtering genes with 0 counts
dds # view number of genes afternormalization and the number of samples
dds <- DESeq(dds) # Differential expression analysis
vsd <- vst(dds, blind=FALSE) ## variance stabilized
#head(assay(vsd),3)
write.csv(assay(vsd), file = "../results/01-vsd.csv", row.names = T)
```

@@

res_summary(c("sex", "female", "male"))
res_summary(c("tissue", "gonad", "pituitary"))
res_summary(c("tissue", "gonad", "hypothalamus"))
res_summary(c("tissue", "pituitary", "hypothalamus"))
```

@@

summary(aov(PC1 ~ sex * treatment * tissue * treatment, data=pcadata)) 
summary(aov(PC2 ~ sex * treatment * tissue * treatment, data=pcadata))

@@

pdf(file="../figures/01-pcaplot12.pdf", width=3.3, height=2.5)
plot(PCA12)
dev.off()
```
